\documentclass{article}

\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{titling}

\titleformat{\section}
  {\normalfont\sffamily\LARGE}
  {}{0em}{}
\titleformat{\subsection}
  {\sffamily\large\uppercase}
  {}{0em}{}
\titleformat{\subsubsection}
  {\normalfont\sffamily\large}
  {}{0em}{}
\titleformat{\subsubsubsection}
  {\normalfont\sffamily}
  {}{0em}{}

\defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
\setmainfont{Lyon Text}
\setsansfont{Calibre Medium}
\pagenumbering{gobble}

\renewcommand{\maketitle}{
  \begin{minipage}[]{.5\textwidth}
    \par{\Huge\sffamily{\theauthor}\par}
  \end{minipage}
  \begin{minipage}[t]{.5\textwidth}
    \emph{Frontend Developer}

    https://www.github.com/ptrfrncsmrph/
    
    peter.francis.murphy@gmail.com
  \end{minipage}
}

\author{Peter Murphy}

\begin{document}

\maketitle

\subsection{Technical Skills}

\paragraph{Languages}

I have experience in JavaScript, Haskell, HTML, and CSS. I am mostly
familiar with frontend technologies, though I have set up basic backends
using Node with Express (in JavaScript), Scotty (in Haskell), and am
currently learning SQL. Libraries I've used in JS include React, Redux,
and D3.

\paragraph{Workflow}

I alternate between VS Code and Vim with tmux. I'm adept at Git and I
also have experience with basic Bash operations and writing Makefiles
for automating workflow. I use Tape and Jest for testing in JavaScript;
in Haskell I use Hspec and have some experience using QuickCheck for
property testing. I very much enjoy test-driven development.

\subsection{Experience}

\subsubsection{Cape Cod Functional Programming
Meetup}

\paragraph{Organizer}

I organize a local meetup group centered around learning functional
programming, mostly in JavaScript as that's our \emph{lingua franca}. I
also maintain a blog for the group, made with Hakyll (a Haskell-based
static site generator) and Markdown, customized to use syntax-highlighted
codeblocks, MathJax, and responsive CSS. The site is hosted with GitLab
pages using the built-in CI: http://ccfp.gitlab.io/blog/.

\subsubsection{SunWind, LLC}

\paragraph{PV System Designer / Energy
Consultant}

I helped develop a single page web application (written in React) for
internal use to help with putting together project proposals. The app is
hosted here: http://sunwindcalc.gitlab.io/.

\subsection{Education}

\subsubsection{Hobart College}

Graduated \emph{cum laude} with a B.A. in Philosophy, minor in
Mathematics.

\end{document}
